---
title: "cards_analysis"
author: "Brandon Leff"
date: "9/13/2019"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(scales)
library(dplyr)
library(forcats)
```

----

# Data Preparation

First we must load in the data.

```{r}
cards <- readxl::read_excel("/Users/brandonleff/Desktop/clashroyale/clashroyale_bnleff/data/cards.xlsx")
```

Now we must change the data type for the `rarity` and `type` variables turning them into factors.

```{r}
cards$rarity <- factor(cards$rarity, labels = c("Common", "Epic", "Legendary", "Rare"))
cards$type <- factor(cards$type, labels = c("Building", "Spell", "Troop"))
```

Now let's double check the data frame is correct now.

```{r}
cards
```

We must relevel the factors in order to understand the data better.

```{r}
cards$rarity <- cards$rarity %>% fct_relevel("Common", "Rare", "Epic", "Legendary")
cards$type <- cards$type %>% fct_relevel("Troop", "Building", "Spell")
```

----

# Univariate Analysis

In order to understand the data better I will do quick plots to show the breakdown of the data.

```{r}
plot_frq(cards$rarity, title = "Clash Royale Card Rarities", ylim = c(0,40), axis.title = c("Rarities", "Frequency")) + scale_fill_brewer() + theme_grey()
```

As seen in the graph above, the highest proportion of cards in Clash Royale are Epic cards with 27 (28.7%) cards in the game. This is followed by Rare cards with 26 (27.7%), Common cards with 24 (25.5%), and lastly Legendary cards with 17 (18.1%).

```{r}
plot_frq(cards$type, title = "Clash Royale Card Types", ylim = c(0,80), axis.title = c("Types", "Frequency")) + scale_fill_brewer() + theme_grey()
```

As seen in the graph above, the highest proportion of cards in Clash Royale are Troop cards with 64 (68.1%) cards in the game. This is followed by Spell cards with 18 (19.1%) and Building cards with 12 (12.8%).







----